Using language as an indicator of cognitive decline in pre-clinical Alzheimer's Disease.

### 2020-01-06 Source/Paper 1 - Presidents Corpus Paper/PresidentsCorpus.tex
edited Presidents Corpus

\bigskip
\begin{abstract}
Several research efforts aimed at improving the early diagnosis of Alzheimer's Disease have focused on the longitudinal analysis of lexical features which have been implicated in the pre-clinical progression of this disease. We build on these studies and continue to refine a method for extracting and analysing language from transcripts. This method is based on a statistical evaluation of the most relevant features, as well as on the use of Generalised Additive Models instead of Linear Regression as a way to more adequately model the declines in language over time. We evaluate this method using the unscripted question and answer portions of news conferences from three U.S Presidents: Ronald Reagan (RR), who would later go on to receive a diagnosis of Alzheimer's Disease; George H. W. Bush (GB) and Donald Trump (DT), who have no known diagnosis of dementia. Our controls were the closest in age to RR when they became president. Our analysis uncovered several lexical features that did not change significantly for GB and DT, but presented significant changes for RR, including significant decreases in unique words and noun usage, and significant increases in pronouns, conjunctions and words which are related to social processes significantly increase over time. We also show that non-linear models provide a more appropriate way to model these changes over time. These findings are consistent with the psychological literature, which documents a link between these features and cognitive decline in Alzheimer's Disease.  This work points the way to developing a comparatively non-invasive protocol that could be used in clinical settings that help to spot atypical declines in language use over time, potentially contributing to earlier, more accurate diagnoses of Alzheimer's Disease.
\end{abstract}

@@

There are different types of dementia including Alzheimer's Disease (AD), vascular dementia, dementia with Lewy bodies and fronto-temporal dementia, all of which are currently incurable. AD is a progressive neurodegenerative disease and is the most common type of dementia, responsible for approximately 60\% to 80\% of all cases \cite{Duong2017}. Currently, a definitive diagnosis for AD can only be produced at post-mortem. However, there are a number of psychological and physiological indicators that can indicate that AD is is present. These physiological changes lead to the development of some of the psychological symptoms associated with AD, primarily cognitive deficits such as problems with episodic and semantic memory, organizing and planning and other problems with executive function, difficulties with language, and visuospatial deficits \cite{McKhann2011}. These cognitive symptoms are often accompanied by emotional problems such as depression and behavioural difficulties. As more neurons die throughout the brain, a person with AD gradually loses the ability to think, remember, make decisions and function independently.

@@

One of the challenges associated with the early detection of AD is differentiating natural age associated memory impairment and cognitive decline due to aging from decline due to AD \cite{Lo2017}. This challenge is often complicated further due to the large variation in the cognitive abilities and educational background of individuals \cite{Harada2013}. The work of Albert et al helps to address this by the development of clinical criteria which professionals can use to diagnose MCI due to AD. One of the most important observations from this piece of work is that a diagnosis of MCI requires evidence of intra-individual change and optimally requires evaluation at two or more points \cite{Albert2011}.This is essentially to place more importance on the trajectory of a person's cognitive abilities rather than a person's cognitive ability in general. 
% Should we say something about the US presidents project. I know you descript it properly in a page or two but the point here is that although speeches easily collected, there is little in the piblic domain that is of good fidelity and that improptu speech of someone who went on to develop AD.

\par 
There has been significant research in the area of language deterioration as a method of detecting AD at an earlier stage. This usually takes the form of recording speech whilst patients' undertake a cognitive assessment such as the Picture Description Task \cite{Fraser2015}. Given that language samples are relatively easy to collect, research has moved towards analysis of spontaneous speech. The work of Berisha and Liss is a good example of this, their study compared the differences in language use between two US presidents, Ronald Reagan (RR), who would go on to receive a diagnosis of Dementia and George H. W. Bush (GHWB) who acted as a matched control based on Age \cite{Berisha2015}. They found several differences in language use over time which they felt acted as indicators of RR's difficulties with language due to AD. Differences in features of language identified to be statistically significant included the number of unique words used per speech, the use of non-specific nouns and fillers and low imageability verbs \cite{Berisha2015}. 
\par   
Berisha and Liss have developed interesting ideas about how we might track changes over time in various lexical features which have been associated with the development of Alzheimer's Disease. However we feel that cognitive decline in pre-clinical AD is not accurately modeled as a linear process.

 and therefore we explored the application of generalised additive models (GAMs) to this data which have no assumed understanding of the distribution of the data. We refine these ideas with the aim of exploring the potential for a protocol that can be used for analyzing language deterioration.

@@

\subsection{Pre-processing}
To generate the files necessary for analysis, we downloaded each transcript and pre-processed each transcript in the following way. We omitted the prepared statement by the president and any speech by other individuals and started each transcript at the beginning of the first answer to a question by a member of the press. We filtered any annotations that were added to the transcript, including any references or clarifications, and any laughter. It is worth noting that there appears to be a difference in how 'hesitations' were marked down between each president. For RR \& DJT hesitations were marked by a single hyphen whereas for GHWB hesitations are marked by a double hyphen. In order to maintain consistency when parsing through the documents, we have changed both types of hesitation to be marked by a single hyphen. We also omitted one word answers to questions as this data would, from a theoretical perspective, not be relevant for language analysis. We did not make any alterations to the length of the document, but instead generated features which would normalise by the length of the document. We therefore were able to include all press conferences by the presidents analysed where there was a question and answer session conducted at least in part by the president (2 press conferences of GHWB were omitted due to a lack of a question and answer session).

\subsection{Feature Generation}
Features were generated by running each transcript through a number of natural language processing libraries. We used the Natural Language ToolKit (NLTK) package \cite{Bird2009} in Python to stem each transcript using the Snowball Stemmer and also completed a part of speech (POS) tagging process. We also ran each transcript through Linguistic Inquiry and Word Count (LIWC) \cite{Pennebaker2015} software. We completed all NLP tasks in Python and completed all statistical analysis in R.. 
\par 
\subsubsection{Measures of lexical diversity}
Lexical diversity is a measure of the variety of language used within a given document and this is commonly used in the literature to measure language declinein those with MCI and AD \cite{Bucks2000, Le2012}. A document is said to have high lexical diversity if the number of unique words is large. We constructed four features of lexical variation. Firstly we looked at the number of unique words. To do this we were able to split each transcript into individual words and changed them to lowercase using NLTK and were then count the number of unique words that appeared in each transcript. We also used the TTR formula, Brunet's Index and Honore's Statistic as other measures of lexical diversity \cite{Bucks2000}. For the formula's below, we use the following notation. N = total number of words, V = number of unique words and V1 = the number of words spoken exactly once.
\par 
Type token ratio (TTR) is the ratio obtained by dividing the types (The total number of different words) by the tokens (the total number of words in an utterance).
\begin{equation} \label{x1}
TTR = V / N
\end{equation}
\par 
Brunet's Index (W) differentiates itself from TTR, as it is not impacted by the length of the text itself. Brunet's Index is defined by the following equation:
\begin{equation} \label{x2}
W = N^{-0.165V}
\end{equation}
 Brunet's Index usually has a score of between 10 and 20, with high numbers indicating a more rich vocabulary compared to low numbers. \newline
\par 
Honore's Statistic is based on the idea that vocabulary richness is implied when a speaker uses a greater amount of unique words. This is indicated by the following equation: 
\begin{equation} \label{x3}
R = (100 \log N) / (1 - V1/V)
\end{equation}
\subsubsection{Fillers, Non-Specific Nouns and Low Imageability Verbs}
Fillers, Non-Specific Nouns and Low Imageability Verbs were features used by Berisha and Liss in their research \cite{Berisha2015} and were taken from work done by Bird et al \cite{Bird2000}. Fillers can be described as a potentially meaningless word that marks a pause or hesitation in speech. In those with MCI and AD, these words can be used to temporarily disguise problems in thought processes or word finding difficulties. Non-Specific Nouns refer to a category or an unspecified member of a given category, once again this can be characterised as a compensatory strategy for word finding difficulties. Imageability is characterized, according to Berisha and Liss\cite{Berisha2015}, as the ease with which a word provokes a mental image of what the word describes.

@@

\subsubsection{Usage of parts of speech}
Using a Part of Speech tagger (PoS) on each transcript analyses each sentence within the transcript and assigns a 'tag' to each word based on the function the word has in a sentence. At a basic level this can be divided into the eight defined parts of speech: 'nouns', 'pronouns', verbs', 'adjectives', 'adverbs', 'conjunctions', 'prepositions' and 'interjections' but can be further subcategorised. We used the PoS tagger built into NLTK to tag each transcript in turn and used these the counts from each of these eight categories in our analysis. In addition to frequency counts we also normalised these features by dividing the frequency count by the number of words in the document to take into account transcript length.

\subsubsection{Linguistic Inquiry and Word Count(LIWC)}
The LIWC is a text processor which analysis words within a given a document and compares the words in the LIWC dictionary file. The LIWC dictionary file contains over 6000 words which are categorised into approximately 90 different types. For example the word 'cried' is part of five word categories: sadness, negative emotion, overall affect, verbs and past focus \cite{Pennebaker2015}. Each word in the document or set of documents is searched for in the dictionary file and if found, the appropriate type is incremented by 1. What is output is an analysis of word usage in reference to each category. This is particularly useful in analysing both structural language changes but also the content or themes of language for a given transcript or set of transcripts.

@@

In terms of more specific language differences between the presidents, as we found that RR used significantly more unique words, non-specific nouns and low imageability verbs than GHWB and DJT (see Table 3). The mean length of utterance for RR was significantly greater than that of GHWB and DJT. Some of these differences are due to the length of the sample, particularly in the case of DJT where his average sample is almost half the sample of RR. It could also be said that this could be down to differences in linguistic abilities or speaking style \cite{Berisha2015, Le2011}. However, we can certainly see that as controls GWHB and DJT are comparative in relation to non-specific nouns and LI verbs.

@@

\subsection{Longitudinal Analysis}
\subsubsection{Comparison of Ronald Reagan and George H.W. Bush}
We then looked at the data from a longitudinal perspective as we were interested seeing whether we can track various language variables and their progress over time. We ran a number of Pearsons correlations with number of days as a time reference (we calculated this as the total number of days from the first sample) and the dependant variables. We also calculated these Pearsons correlations with transcript index number as a time reference and the dependant variables as a replication of the Berisha and LIss study \cite{Berisha2015} and these results are described in the supplementary material.

For our controls, we found them to be stable for the most part with the main highlights being a decrease in Adverb usage for DJT (R=-0.36, p=0.049) and a steady but not severe decline in a number of variables for GWHB, namely total word count, unique words, low imageability words and verb usage.
\par 
For RR, his decline is more marked and more widespread through his language use. We noticed an significant increase in adverb (R=0.41, p=0.004) and pronoun usage (R=0.65, p\textless0.001), as well as a slight usage increase in Non-specific nouns(R=0.30, p=0.03). There was also a significant decrease in number of unique words (R=-0.56, p\textless0.001) and noun usage (R=-0.70, p\textless0.001). Also very significant decrease in adjective usage (R=-0.40, p=0.005) and a significant decrease in total word count (R=-0.31, p=0.03). 
\par
Given the number of hypotheses being tested, we felt it was necessary to control for false discovery rate and therefore Benjamii-Yekutieli procedure was applied to the results of the analysis. By applying this, we produced a final list of important features for each president. For RR, this was 22 features and for GHWB this was 14 features.  The features were generated from multiple sources and therefore there was some significant overlap between the features but for completeness we have included all features in Table 6.

@@

\subsubsection{Comparison of Ronald Reagan and Donald J. Trump}
\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | l | c | c |}
		\hline
		& RR R-Squared & DJT R-Squared \\ \hline
		ppron & \textbf{0.700***} & 0.007 \\ \hline
		social & \textbf{0.698***} & 0.204 \\ \hline
		NounsNormalised & \textbf{-0.689***} & -0.023 \\ \hline
		function & \textbf{0.670***} & -0.169 \\ \hline
		conj &\textbf{0.644***} & -0.452 \\ \hline
		PronounsNormalised & \textbf{0.631***} & 0.131 \\ \hline
		Analytic & \textbf{-0.626***} & -0.013 \\ \hline
		NN & \textbf{-0.601***} & -0.197 \\ \hline
		male & \textbf{0.585***} & 0.024 \\ \hline
		UniqueWords & \textbf{-0.578***} & -0.257 \\ \hline
		WDT & \textbf{-0.577***} & -0.173 \\ \hline
		shehe & \textbf{0.529*} & -0.005 \\ \hline
		VBZ & \textbf{-0.521*} & -0.157 \\ \hline
		JJ & \textbf{-0.518*} & -0.206 \\ \hline
		Fillers & -0.076 & \textbf{-0.359**} \\ \hline	
		EX & -0.193* & \textbf{-0.337**} \\ \hline	
		achieve & -0.248 & \textbf{0.334**} \\ \hline		
		\multicolumn{3}{@{}p{1.5in}}{\footnotesize * denotes p\textless 0.05} \\
    	\multicolumn{3}{@{}p{1.5in}}{\footnotesize ** denotes p\textless 0.01} \\
    	\multicolumn{3}{@{}p{1.5in}}{\footnotesize *** denotes p\textless 0.001} \\
	\end{tabular}
	\caption{\label{tab:table-name}Pearson Correlations for Features}
	\end{center} 
\end{table}

>>>>

\bigskip
\begin{abstract}
Several research efforts aimed at improving the early diagnosis of Alzheimer's Disease have focused on the longitudinal analysis of lexical features which have been implicated in the pre-clinical progression of this disease. We build on these studies to develop a refined method for extracting and analysing language from transcripts. Our method is based on a statistical evaluation of the most relevant features, as well as on the use of Generalised Additive Models instead of Linear Regression as a way to more adequately model the declines in language over time. We evaluate our method using the unscripted question and answer portions of news conferences from three U.S Presidents: Ronald Reagan (RR), who would later go on to receive a diagnosis of Alzheimer's Disease; George H. W. Bush (GB) and Donald Trump (DT), who have no known diagnosis of dementia. Our controls were the closest in age to RR when they became president. Our analysis uncovered several lexical features that did not change significantly for GB and DT, but presented significant changes for RR. These included decreases in unique words and noun usage, and significant increases in pronouns and conjunctions and also words which are related to social processes significantly increase over time. We also show that non-linear models provide a more detailed way to model these changes over time that is sensitive to variability in the degrees of change that is typical of AD. Our findings are consistent with the psychological literature, which documents a link between these features and cognitive decline in Alzheimer's Disease. This work demonstrates that there are potentially a wider number of language markers that researchers can track, which may indicate the presence of mild cognitive impairment as well as illustrating a more nuanced way of modelling these changes via Generalised Additive Models.
\end{abstract}

@@

There are different types of dementia including Alzheimer's Disease (AD), vascular dementia, dementia with Lewy bodies and fronto-temporal dementia, all of which are currently incurable. AD is a progressive neurodegenerative disease and is the most common type of dementia, responsible for approximately 60\% to 80\% of all cases \cite{Duong2017}. Currently, a definitive diagnosis for AD can only be produced post-mortem. However, there are a number of psychological and physiological indicators that can indicate that AD is is present. These physiological changes lead to the development of some of the psychological symptoms associated with AD, primarily cognitive deficits such as problems with episodic and semantic memory, organizing and planning and other problems with executive function, difficulties with language, and visuospatial deficits \cite{McKhann2011}. These cognitive symptoms are often accompanied by emotional problems such as depression and behavioural difficulties. As more neurons die throughout the brain, a person with AD gradually loses the ability to think, remember, make decisions and function independently.

@@

One of the challenges associated with the early detection of AD is differentiating natural age associated memory impairment and cognitive decline due to aging from decline due to AD \cite{Lo2017}. This challenge is often complicated further due to the large variation in the cognitive abilities and educational background of individuals \cite{Harada2013}. The work of Albert et al helps to address this by the development of clinical criteria which professionals can use to diagnose MCI due to AD. One of the most important observations from this piece of work is that a diagnosis of MCI requires evidence of intra-individual change and optimally requires evaluation at two or more points \cite{Albert2011}.This is essentially to place more importance on the trajectory of a person's cognitive abilities rather than a person's cognitive ability in general. Berisha and Liss used the transcripts of press conferences of Ronald Reagan who would go on to be diagnosed with AD, and George Bush Sr who had no diagnosis. These speeches are in the public domain and provide a good opportunity of analysing the spontaneous language use of someone with AD, before a diagnosis was made. 
There has been significant research in the area of language deterioration as a method of detecting AD at an earlier stage. This usually takes the form of recording speech whilst patients' undertake a cognitive assessment such as the Picture Description Task \cite{Fraser2015}. Given that language samples are relatively easy to collect, research has moved towards analysis of spontaneous speech. The work of Berisha and Liss is a good example of this, their study compared the differences in language use between two US presidents, Ronald Reagan (RR), who would go on to receive a diagnosis of Dementia and George H. W. Bush (GHWB) who acted as a matched control based on Age \cite{Berisha2015}. They found several differences in language use over time which they felt acted as indicators of RR's difficulties with language due to AD. Differences in features of language identified to be statistically significant included the number of unique words used per speech, the use of non-specific nouns and fillers and low imageability verbs \cite{Berisha2015}. 
% Stronger motivation
Berisha and Liss have developed interesting ideas about how we might track changes over time in various lexical features which have been associated with the development of Alzheimer's Disease. However we feel that cognitive decline in pre-clinical AD is not accurately modeled as a linear process and therefore we explored the application of generalised additive models (GAMs) to this data which have no assumed understanding of the distribution of the data. We refine these ideas with the aim of exploring the potential for a protocol that can be used for analyzing language deterioration.

@@

\subsection{Pre-processing}
To generate the files necessary for analysis, we downloaded each transcript and pre-processed each transcript in the following way. We omitted the prepared statement by the president and any speech by other individuals and started each transcript at the beginning of the first answer to a question by a member of the press. We filtered any annotations that were added to the transcript, including any references or clarifications, and any laughter. It is worth noting that there appears to be a difference in how 'hesitations' were marked down between each president. For RR \& DJT hesitations were marked by a single hyphen whereas for GHWB hesitations are marked by a double hyphen. In order to maintain consistency when parsing through the documents we changed both types of hesitation to be marked by a single hyphen. We also omitted one word answers to questions as this data would, from a theoretical perspective, not be relevant for language analysis. We did not make any alterations to the length of the document, but instead generated features which would normalise by the length of the document. We were therefore able to include all press conferences by the presidents analysed where there was a question and answer session conducted at least in part by the president (2 press conferences of GHWB were omitted due to a lack of a question and answer session).

\subsection{Feature Generation}
% We selected the type of processing as
Features were generated by running each transcript through a number of natural language processing libraries. We used the Natural Language ToolKit (NLTK) package \cite{Bird2009} in Python to stem each transcript using the Snowball Stemmer and also completed a part of speech (POS) tagging process. We also ran each transcript through Linguistic Inquiry and Word Count (LIWC) \cite{Pennebaker2015} software. We completed all NLP tasks in Python and completed all statistical analysis in R.. 
\par 
\subsubsection{Measures of lexical diversity}
Lexical diversity is a measure of the variety of language used within a given document and this is commonly used in the literature to measure language declinein those with MCI and AD \cite{Bucks2000, Le2012}. A document is said to have high lexical diversity if the number of unique words is large. We constructed four features of lexical variation. Firstly we looked at the number of unique words. To do this we split each transcript into individual words and changed them to lowercase using the NLTK package and were then count the number of unique words that appeared in each transcript. We also used the TTR formula, Brunet's Index and Honore's Statistic as other measures of lexical diversity \cite{Bucks2000}. For the formula's below, we use the following notation. N = total number of words, V = number of unique words and V1 = the number of words spoken exactly once.
\par 
Type token ratio (TTR) is the ratio obtained by dividing the types (The total number of different words) by the tokens (the total number of words in an utterance).
\begin{equation} \label{x1}
TTR = V / N
\end{equation}
\par 
Brunet's Index (W) differentiates itself from TTR, as it is not impacted by the length of the text itself. Brunet's Index is defined by the following equation:
\begin{equation} \label{x2}
W = N^{-0.165V}
\end{equation}
 Brunet's Index usually has a score of between 10 and 20, with high numbers indicating a more rich vocabulary compared to low numbers. \newline
\par 
Honore's Statistic is based on the idea that vocabulary richness is implied when a speaker uses a greater amount of unique words. This is indicated by the following equation: 
\begin{equation} \label{x3}
R = (100 \log N) / (1 - V1/V)
\end{equation}
\subsubsection{Fillers, Non-Specific Nouns and Low Imageability Verbs}
Fillers, Non-Specific Nouns and Low Imageability Verbs were features used by Berisha and Liss in their research \cite{Berisha2015} and were taken from work done by Bird et al \cite{Bird2000}. Fillers can be described as a potentially meaningless word that marks a pause or hesitation in speech. In those with MCI and AD, these words can be used to temporarily disguise problems in thought processes or word finding difficulties. Non-Specific Nouns refer to a category or an unspecified member of a given category, once again this can be characterised as a compensatory strategy for word finding difficulties. Imageability is characterized, according to Berisha and Liss\cite{Berisha2015}, as the ease with which a word provokes a mental image of what the word describes.

@@

\subsubsection{Usage of parts of speech}
Using a Part of Speech tagger (PoS) on each transcript analyses each sentence within the transcript and assigns a 'tag' to each word based on the function the word has in a sentence. At a basic level this can be divided into the eight defined parts of speech: 'nouns', 'pronouns', verbs', 'adjectives', 'adverbs', 'conjunctions', 'prepositions' and 'interjections' but can be further subcategorised. We used the PoS tagger built into NLTK to tag each transcript in turn and used the counts from each of these eight categories in our analysis. In addition to frequency counts we also normalised these features by dividing the frequency count by the number of words in the document to take into account transcript length.

\subsubsection{Linguistic Inquiry and Word Count(LIWC)}
The LIWC is a text processor / semantic tagger which analysis words within a given a document and compares the words in the LIWC dictionary file. The LIWC dictionary file contains over 6000 words which are categorised into approximately 90 different types. For example the word 'cried' is part of five word categories: sadness, negative emotion, overall affect, verbs and past focus \cite{Pennebaker2015}. Each word in the document or set of documents is searched for in the dictionary file and if found, the appropriate types is incremented by 1. What is output is an analysis of word usage in reference to each category. This is particularly useful in analysing both structural language changes but also the content or themes of language for a given transcript or set of transcripts.

@@

In terms of more specific language differences between the presidents, as we found that RR used significantly more unique words, non-specific nouns and low imageability verbs than GHWB and DJT (see Table 3). The mean length of utterance for RR was significantly greater than that of GHWB and DJT. Some of these differences are due to the length of the sample, particularly in the case of DJT where his average sample is almost half the sample of RR. It could also be said that this could be due to differences in linguistic abilities or speaking style \cite{Berisha2015, Le2011}. However, we can certainly see that as controls GWHB and DJT are comparative in relation to non-specific nouns and LI verbs.

@@

\subsection{Longitudinal Analysis}
\subsubsection{Comparison of Ronald Reagan and George H.W. Bush}
We then looked at the data from a longitudinal perspective as we were interested in seeing whether we can track various language features and their progress over time. We ran a number of Pearsons correlations with number of days as a time reference (we calculated this as the total number of days from the first sample) and the dependent variables. We also calculated these Pearsons correlations with transcript index number as a time reference and the dependant variables as a replication of the Berisha and LIss study \cite{Berisha2015} and these results are described in the supplementary material.

For our controls, we found them to be stable for the most part with the main highlights being a decrease in Adverb usage for DJT (R=-0.36, p=0.049) and a steady but not severe decline in a number of variables for GWHB, namely total word count, unique words, low imageability words and verb usage.
\par 
For RR, his decline is more marked and more widespread through his language use. We noticed an significant increase in adverb (R=0.41, p=0.004) and pronoun usage (R=0.65, p\textless0.001), as well as a slight usage increase in Non-specific nouns(R=0.30, p=0.03). There was also a significant decrease in number of unique words (R=-0.56, p\textless0.001) and noun usage (R=-0.70, p\textless0.001). Also there was a significant decrease in adjective usage (R=-0.40, p=0.005) and a significant decrease in total word count (R=-0.31, p=0.03). 
\par
Given the number of hypotheses being tested, we felt it was necessary to control for false discovery rate and therefore Benjamii-Yekutieli procedure was applied to the results of the analysis. By applying this, we produced a final list of important features for each president. For RR, this was 22 features and for GHWB this was 14 features.  The features were generated from multiple sources and therefore there was some significant overlap between the features but for completeness we have included all features in Table 6.

@@

\subsubsection{Comparison of Ronald Reagan and Donald J. Trump}
\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | l | c | c |}
		\hline
		& RR R-Squared & DJT R-Squared \\ \hline
		ppron & \textbf{0.700***} & 0.007 \\ \hline
		social & \textbf{0.698***} & 0.204 \\ \hline
		NounsNormalised & \textbf{-0.689***} & -0.023 \\ \hline
		function & \textbf{0.670***} & -0.169 \\ \hline
		conj &\textbf{0.644***} & -0.452 \\ \hline
		PronounsNormalised & \textbf{0.631***} & 0.131 \\ \hline
		Analytic & \textbf{-0.626***} & -0.013 \\ \hline
		NN & \textbf{-0.601***} & -0.197 \\ \hline
		male & \textbf{0.585***} & 0.024 \\ \hline
		UniqueWords & \textbf{-0.578***} & -0.257 \\ \hline
		WDT & \textbf{-0.577***} & -0.173 \\ \hline
		shehe & \textbf{0.529*} & -0.005 \\ \hline
		VBZ & \textbf{-0.521*} & -0.157 \\ \hline
		JJ & \textbf{-0.518*} & -0.206 \\ \hline
		Fillers & -0.076 & \textbf{-0.359**} \\ \hline	
		EX & -0.193* & \textbf{-0.337**} \\ \hline	
		achieve & -0.248 & \textbf{0.334**} \\ \hline		
		\multicolumn{3}{@{}p{1.5in}}{\footnotesize * denotes p\textless 0.05} \\
    	\multicolumn{3}{@{}p{1.5in}}{\footnotesize ** denotes p\textless 0.01} \\
    	\multicolumn{3}{@{}p{1.5in}}{\footnotesize *** denotes p\textless 0.001} \\
	\end{tabular}
	\caption{\label{tab:table-name}Pearson Correlations for Features}
	\end{center} 
\end{table}
% Needs explanation
